Extract and Store Some Data
========================================================

We'll first want to install the `curatedOvarianData` package from Bioconductor. Note that this package is a few hundred MB.

```{r, cache=TRUE, results='hide', message=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite("curatedOvarianData")
```

Now we'll load the package and load in one of the datasets.

```{r, results='hide', message=FALSE}
library(curatedOvarianData)
data(TCGA_eset)
```

Let's write out the clinical data so we have it for later. We'll trim out the "uncurated" metadata column to save some space and make the printing a bit easier.

```{r}
clinical <- pData(TCGA_eset)
clinical <- clinical[,colnames(clinical)!="uncurated_author_metadata"]
```

We won't want to store all of the tumor samples available in the dataset, so let's grab 20 tumor samples at random and keep all of the normal samples.

```{r}
normalClinical <- clinical[clinical$sample_type == "adjacentnormal",]

tumorIndices <- sample(which(clinical$sample_type == "tumor"), 20)
tumorClinical <- clinical[tumorIndices,]
saveRDS(tumorClinical, "tumorClinical.Rds")
```

Filtering
---------

For the sake of demonstration, we'll want to keep the dataset fairly small. So let's filter the data to the few dozen samples we selected above and only 8 genes.

```{r}
geneList <- c("EGFR", "KLF6", "FOXO1", "KRAS", "JAK2", "BRCA1", "BRCA2", "PPM1D")
```

```{r}
tumor <- exprs(TCGA_eset[,tumorIndices])
tumor <- tumor[match(geneList, rownames(tumor)),]
saveRDS(tumor, "tumorExpr.Rds")
```


And grab all of the normal tissue samples:

```{r}
normal <- exprs(TCGA_eset[,TCGA_eset@phenoData@data$sample_type == "adjacentnormal"])
normal <- normal[match(geneList, rownames(normal)),]
saveRDS(normal, "normalExpr.Rds")
```

Now we should be able to use this sampled data from our apps!
